The limits of self commitment and private paternalism \thanks{}

### 2022-01-26 donde.tex
Figure 8 - panel (d)
checkpoint before edits of tables and figues

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
\date{This draft:  \today \\[2 cm]}

@@

% \section{Introduction}

Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems. For instance, ``[mortgages restrict choice] with a fixed repayment stream and mandatory principal repayment'' \citep{Laibson2018}.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud and don't market these commitment features, presumably because students, workers and borrowers don't welcome these restrictions. \cite{Laibson2018} argues that this presents an important puzzle: clients that would benefit from commitment underestimate its value and thus have low demand for it. In such a case private paternalism may be beneficial.\footnote{Laibson defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions. %In this paper we will study the effect of restricting freedom of contract choice on two outcomes: pawn recovery and financing cost, not overall welfare.
We want to clarify that we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into installment contracts instead of letting them choose. We are not making claims about overall welfare which is a slippery concept if we take into account the possibility of biased beliefs and preferences.}

This paper studies the benefits of restricting choice in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues. In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts. The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange for an immediate cash loan of a smaller value. In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value. The contract stipulates a 7\% monthly interest rate charged daily, a loan term of 90 days, and the flexibility to pay back the loan at anytime before the loan is due. In spite of this flexibility ---or perhaps because of it--- 60\% of clients lose their pawn\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}, and among those that recover it almost all of them pay in the days just before the loan elapses.

@@

We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City. We answer five main questions using this experiment. First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract? That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost. Second, would there be demand for such an installment contract vis-a-vis the status quo one if given the choice? Note that any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the former provides commitment. Third, would clients who benefit from commitment the most (e.g. the present biased or overconfident) demand it more? Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility? Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{%Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}. 
There is some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing clients into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn? Or on the contrary, is it better to force the installment contract 
paternalistically?

The experiment involved 5 arms, with randomization happening at the branch-day level. It is described in detail in Section \ref{Experiment}. Here let us briefly explain the main 3 arms. The first one involves a group of clients that were given only the status quo flexible payments contract (henceforth the \textit{status-quo forcing group}). The second arm (\textit{fee-forcing group}) was given a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length. Failing to do this would result in a fee of 2\% of the amount due that month. A third group (\textit{Fee-choice group}) gave clients a choice between these two contracts.

Results are striking. First, we find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by 9.4\% on average (from \$3157 to \$2860 MXN), while the likelihood of recovering their pawn increases by 26\% (from 43\% to 55\%). Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and notably, those we classify as overconfident, experience larger gains. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. That is, the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.

@@

Second, in spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low. Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former. This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two project assistants in each of the experimental branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences. Furthermore take up is systematically predicted by baseline covariates, making it less likely that these are just random mistakes.} We show further that clients that most benefit from the contract (those who are overconfident about recovering) are \textit{less} likely to demand it, echoing a result by \cite{Sprenger} for grocery purchases and \cite{Walters} for schools. %is Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}). 
%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment. \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem. Close to ninety percent of our subjects claim to have pawned before. We find that experience does not predict positive take up in our sample.} 
%\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them. 
Owing to this low take-up, we estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery throughout the quantile distribution.

@@

Third, combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients. We calculate that about {80}\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \${238} MXN, close to {11}\% of the average loan value. In particular {92}\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only {8}\% of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts ---private paternalism--- may be beneficial for the overwhelming majority of clients. After seeing our results Lender $P$ introduced frequent payment contracts in their loans portfolio.

Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of (partly) naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' product in the form of a salient promise to pay.  \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior. %and also induces trusting behavior by the recipients of the promise.

To measure the causal effect of promises we implemented two other treatment arms. A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there was a fee if they didn't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and not kept their word. Because salience is key we made them sign a (legally non-binding) personal promise and emphasized that we were counting on them to keep their promise. A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise} contract and the \textit{Status-quo} contract.

We document three main results in the promise arms. First, demand for the promise-commitment contract is three times larger than for the fee-commitment contract, with {31}\% take-up. This difference shows that clients are indeed taking into account the contractual parameters when they choose, and that the fee commitment was probably too strong from their point of view. Second, in spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising. Third, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery. %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
Promises did not provide enough commitment so as to be reflected in behavior. This is one of the first  experiments using promises in the field, and results are in striking contrast with those in the lab.

This paper contributes to several strands of literature. First, we focus on an important new context: pawnshop borrowing. Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it (\url{https://tinyurl.com/ydgob8pv}). We could not find peer-reviewed papers about it either.} It is different from microfinance in that it deals with emergency loans, and not loans for productive investment. Because of this, it may draw on a more vulnerable (and potentially more unsophisticated) population, and because it is not typically used for productive investment, the trade-off between loan rigidity and investment found for microfinance \citep{Field} may not be there.

Second, a significant literature has shown that demand for commitment exists. But while it is low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), it is high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). We add to this literature by adding evidence from another market. Demand for commitment  is low, and very small fees\footnote{For instance our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and 5 times smaller converting peso values using exchange rates.} are enough to drastically reduce demand for commitment, even when commitment is cost-reducing. Softer commitment contracts in the form of promises do increase demand but did not change outcomes. %We also show that softer commitments in the form of non-pecuniary personal promises elicit higher demand but do not affect behavior or financing costs.

>>>>

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); McIntosh:  University of California San Diego, ctmcintosh@ucsd.edu; Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
\date{This draft:  \today \\[2 cm]}

@@

\section{Introduction}
Many people have a difficult time accumulating and retaining capital unless they are provided a structure within which to do so.  The behavioral lens on intertemporal financial services has provided critical insights on this problem, suggesting that saving from cash-in-hand is challenging \citep{Ashraf, Pascaline}, that credit may be preferred to savings as a way of accumulating capital simply because credit repayment contracts provide more structure \cite{Murdoch}, and even that the absence of structured financial contracts may be a key barrier preventing the poor from climbing out of poverty \citep{bertrand2004behavioral, collins2009portfolios}.  A large behavioral literature has illustrated that the addition of commitment-style product features improves the ability to accumulate savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters} and to retire debt \citep{Bertrand, heidhues2010exploiting}.  As a consequence, credit markets featuring limited-liability loans such as small-business financing or microfinance typically take a highly structured approach to credit contracts with frequent repayments and reminders as a way of inducing repayment.  As pointed out by \cite{Laibson2018}, because many of these forms of commitment may be desirable to principals but not demanded by agents (or by the right agents), these mechanisms are often ‘shrouded’, meaning that commitment is embedded in products in ways that are not advertised to clients as such.

In this paper we examine pawn contracts, an understudied form of credit despite their relative ubiquity \citep{carter2012pawnshops}, and a major vehicle through which poor households may dis-accumulate savings.  There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.  In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner, a Mexican pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.  Pawnshop lending presents an inverted lending case:  since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.  Our collaborating lender gave only 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due.  This combination of features means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).  While an older literature considers the exploitative potential in over-collateralization and underpricing of collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.  When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments that represent the opposite of what the behavioral literature tells us will induce repayment.  To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment to induce default in a manner not obvious to borrowers.  Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have first-order consequences for the financial lives of the poor.

Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of commitment in pawn repayment contracts.  Our control arm illustrates the costs of the status quo contract; fully 57\% of borrowers default and so lose their pawn.  We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt in to a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments.  In addition, we include a `forced commitment’ arm, in which all borrowers are required to repay using the commitment structure.  The combination of voluntary and forced commitment in the same study allows us to address several key questions.  First, does using more structured repayment contracts help pawnshop borrowers to achieve higher repayment rates, thereby saving them money?  Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers to meaningfully change repayment behavior?  Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the treatment on compliers and the treatment on non-compliers by comparison across the control, choice, and forced arms.

Our results suggest that the structure of the commitment is strongly effective in preventing default, with the average individual in the forced arm paying financing costs inclusive of fees that are 9.4\% lower than the control (from \$3157 to \$2860 MXN), while the likelihood of recovering their pawn increases by 26\% (from 43\% to 55\%).  Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, suggesting that in the context of a commitment structure it is possible to save borrowers money by charging them fees!  Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and those most overconfident about their probability of repayment, experience larger gains.\footnote{As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting.}  Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.

Borrowers assigned to the forced commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.  However, when offered the choice of commitment, very few borrowers elect to commit voluntarily.  Only 10\% of the choice arm takes up the contract, and none of the core study outcomes are significantly improved by the ability to choose commitment.

Most importantly, our multi-arm design allows us to show that the \textit{wrong} people choose commitment when offered it.   We illustrate this point in three distinct ways.  First, we use a Random Forest algorithm \citep{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.  93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.  Second, a Boosted Classification Algorithm arrives at a similar answer, showing that the borrowers naturally cluster into two groups, one of which is likely to choose commitment and does not benefit from it, and the other the reverse.  Finally, estimating LATEs on compliers and non-compliers alike we show that the estimated treatment effect on non-compliers is larger than the treatment effect on compliers.  That is, those choosing commitment benefit less from commitment than those not choosing it.  Hence our results show clearly that a paternalistic policy forcing borrowers into a more rigid and structured repayment regimen is uniquely beneficial to them.  While this perverse relationship between choice and benefits from commitment echo closely the findings of \cite{Sprenger} we are the first to be able to examine this relationship using a high-stakes, money-metric outcome in a natural field environment.

Additional evidence of the importance of paternalism in pawnshop commitment is provided by two additional study arms offering variants of `soft' commitment.  In one arm all borrowers were asked to commit to make three monthly payments instead of a single balloon payment, but no external reminders or fees were imposed.  In a second borrowers were given the ability to choose whether to engage in this form of soft commitment.  Both of these arms are completely ineffective, suggesting that it is the combination of external imposition of the contract along with the teeth provided by the reminder and fees that generate the savings to borrowers relative to the status quo contract.

What explains the persistence of a contract so contrary to borrowers’ interests?  First, we show substantial levels of over-optimism among borrowers.  Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.  While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.  Finally, while we are working with a lender who has a social mission and is interested in understanding how to help borrowers, there is no free lunch.  The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates.  By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate; we estimate that over 50\% of the borrowers in our study are naïve hyperbolics in the sense that they would benefit from commitment but will not choose it.  While our results are driven by the intersection of overcollateralization and a potential selection of the borrower pool towards myopia and short-term financial thinking, these attributes are likely to be present in many types of pro-poor financial markets where individuals lack the credit histories to be able to leverage short-term credit without collateral.  This suggests that regulators of such markets would do well to consider the broader financial costs of lending products, including what is paid through equilibrium default, and to consider imposing more structured lending products that tilt the scales towards allowing borrowers to repay.  While commitment-style repayment contracts decrease effective liquidity by requiring faster repayment of a given loan, the improvement in expected borrower returns are so substantial as to prove welfare improving at all but the most astronomical discount rates.

These conclusions speak to several strands of the literature.  First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases.  While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed over the top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure.  Second, we broaden the analysis of the extent to which voluntary commitment mechanisms are desirable.  Like our study, commitment demand has been found to be low in a number of contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and by illustrating a mechanism for the failure of self-commitment (over-optimism) we may help contextualize those studies in which demand has been found to be more robust (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). Finally, we provide only the second case in the literature, and the first in the analysis of financial products, to illustrate the perverse result that those who opt into commitment are precisely the individuals who do not need it \citep{Sprenger}.

The remainder of the paper is structured as follows:  section \ref{context} provides context and describes the data sources. Section \ref{Data} presents summary statistics and defines our main outcome variables. Section \ref{Experiment} describes the experiment and shows pre-treatment balance across arms. Section \ref{fee-commitment} estimates the effect of forcing clients into the fee-commitment contract, while Section \ref{fee-choice} studies the effects of choice. Section \ref{conclusion} concludes.

%\section{Old Introduction}

%Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems. For instance, ``[mortgages restrict choice] with a fixed repayment stream and mandatory principal repayment'' \citep{Laibson2018}.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud and don't market these commitment features, presumably because students, workers and borrowers don't welcome these restrictions. \cite{Laibson2018} argues that this presents an important puzzle: clients that would benefit from commitment underestimate its value and thus have low demand for it. In such a case private paternalism may be beneficial.\footnote{Laibson defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions. %In this paper we will study the effect of restricting freedom of contract choice on two outcomes: pawn recovery and financing cost, not overall welfare.
%We want to clarify that we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into installment contracts instead of letting them choose. We are not making claims about overall welfare which is a slippery concept if we take into account the possibility of biased beliefs and preferences.}

%This paper studies the benefits of restricting choice in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues. In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts. The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange for an immediate cash loan of a smaller value. In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value. The contract stipulates a 7\% monthly interest rate charged daily, a loan term of 90 days, and the flexibility to pay back the loan at anytime before the loan is due. In spite of this flexibility ---or perhaps because of it--- 60\% of clients lose their pawn\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}, and among those that recover it almost all of them pay in the days just before the loan elapses.

@@

%We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City. We answer five main questions using this experiment. First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract? That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost. Second, would there be demand for such an installment contract vis-a-vis the status quo one if given the choice? Note that any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the former provides commitment. Third, would clients who benefit from commitment the most (e.g. the present biased or overconfident) demand it more? Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility? Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{%Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}. 
%There is some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing clients into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn? Or on the contrary, is it better to force the installment contract paternalistically?

%The experiment involved 5 arms, with randomization happening at the branch-day level. It is described in detail in Section \ref{Experiment}. Here let us briefly explain the main 3 arms. The first one involves a group of clients that were given only the status quo flexible payments contract (henceforth the \textit{status-quo forcing group}). The second arm (\textit{Forced Commitment group}) was given a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length. Failing to do this would result in a fee of 2\% of the amount due that month. A third group (\textit{Commitment Choice group}) gave clients a choice between these two contracts.

%Results are striking. First, we find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by 9.4\% on average (from \$3157 to \$2860 MXN), while the likelihood of recovering their pawn increases by 26\% (from 43\% to 55\%). Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and notably, those we classify as overconfident, experience larger gains. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
%Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. That is, the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.

@@

%Second, in spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low. Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former. This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two project assistants in each of the experimental branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences. Furthermore take up is systematically predicted by baseline covariates, making it less likely that these are just random mistakes.} We show further that clients that most benefit from the contract (those who are overconfident about recovering) are \textit{less} likely to demand it, echoing a result by \cite{Sprenger} for grocery purchases and \cite{Walters} for schools. %is Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}). 
%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment. \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem. Close to ninety percent of our subjects claim to have pawned before. We find that experience does not predict positive take up in our sample.} 
%\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them. 
%Owing to this low take-up, we estimate zero average treatment effects of the \textit{Commitment Choice} arm on financial cost and on pawn recovery throughout the quantile distribution.

@@

%Third, combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients. We calculate that about {80}\% of clients in the Commitment Choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \${238} MXN, close to {11}\% of the average loan value. In particular {92}\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only {8}\% of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts ---private paternalism--- may be beneficial for the overwhelming majority of clients. After seeing our results Lender $P$ introduced frequent payment contracts in their loans portfolio.

%Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of (partly) naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' product in the form of a salient promise to pay.  \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior. %and also induces trusting behavior by the recipients of the promise.

%To measure the causal effect of promises we implemented two other treatment arms. A \textit{promise-forcing} arm exactly analogous to our \textit{Forced Commitment arm} except that instead of telling them that there was a fee if they didn't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and not kept their word. Because salience is key we made them sign a (legally non-binding) personal promise and emphasized that we were counting on them to keep their promise. A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise} contract and the \textit{Status-quo} contract.

%We document three main results in the promise arms. First, demand for the Soft Commitment contract is three times larger than for the fee-commitment contract, with {31}\% take-up. This difference shows that clients are indeed taking into account the contractual parameters when they choose, and that the fee commitment was probably too strong from their point of view. Second, in spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising. Third, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery. %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced Soft Commitment arm however.} Promises did not provide enough commitment so as to be reflected in behavior. This is one of the first  experiments using promises in the field, and results are in striking contrast with those in the lab.

%This paper contributes to several strands of literature. First, we focus on an important new context: pawnshop borrowing. Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it (\url{https://tinyurl.com/ydgob8pv}). We could not find peer-reviewed papers about it either.} It is different from microfinance in that it deals with emergency loans, and not loans for productive investment. Because of this, it may draw on a more vulnerable (and potentially more unsophisticated) population, and because it is not typically used for productive investment, the trade-off between loan rigidity and investment found for microfinance \citep{Field} may not be there.

%Second, a significant literature has shown that demand for commitment exists. But while it is low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), it is high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). We add to this literature by adding evidence from another market. Demand for commitment  is low, and very small fees\footnote{For instance our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and 5 times smaller converting peso values using exchange rates.} are enough to drastically reduce demand for commitment, even when commitment is cost-reducing. Softer commitment contracts in the form of promises do increase demand but did not change outcomes. %We also show that softer commitments in the form of non-pecuniary personal promises elicit higher demand but do not affect behavior or financing costs.
